\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-20 motivation.tex
updates to motivation

To uncover this bug and many other similar ones, the developers are in constant search of a generic and systematic approach for testing distributed storage systems.

>>>>

To uncover this bug, and other tricky ones, the developers are in constant search of a generic and systematic approach for testing distributed storage systems.
